\documentclass[]{debjitpal-resume}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.35\textwidth} 
\begin{large}
	\headername{Debjit Pal}\\
\end{large}
Pre-final Year (B.Tech)\\
Computer Science $\&$  Engineering\\ 
at Kalyani Government Engineering College \\ 
CGPA : 9.11 till 3rd Sem 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
\noindent\rule{5cm}{0.4pt}

Github : \href{https://github.com/debjitpal5040}{\custombold{debjitpal5040}} \\
LinkedIn : \href{https://www.linkedin.com/in/debjit-pal-539214192/}{\custombold{debjitpal5040}} \\
Twitter : \href{https://www.twitter.com/debjitpal5040}{\custombold{debjitpal5040}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{OS}
macOs, Windows
\vspace{6pt}
\subsection{Languages}
Python, R, Swift, C/C++, HTML, CSS
\vspace{6pt}
\subsection{Others}
Markdown, Git, Docker, LaTeX \\
VS Code, PyCharm \\
Xcode, Android Studio \\
CorelDraw, Photoshop, iMovie
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Data Structures\\
Algorithms\\
Formal Language and Automata \\
Discrete Mathematics\\
Operating Systems\\
Computer Architecture\\
Data Analysis
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{2019-2023}
\subsection{B.Tech. in CSE}
\custombold{Kalyani Government Engineering College} \\
SGPA: 8.08 / 10 (First Semester)\\
SGPA: 9.71 / 10 (Second Semester)\\
SGPA: 9.55 / 10 (Third Semester)\\
\vspace{8pt}
\datecolor{2017-2018}
\subsection{Higher Secondary}
\custombold{Uttarpara Government High School}\\
Total Marks Obtained : 455/500 \\
Aggregate Percentage : 91\%\\
\vspace{8pt}
\datecolor{2011-2016}
\subsection{Secondary}
\custombold{Baranagore Ramakrishna Mission Ashrama High School}\\
Total Marks Obtained : 622/700 \\
Aggregate Percentage : 88.85\%
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.6\textwidth} 
% \descript{BTech in Computer Science}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill 105, D.D. Mondal Ghat Road, Dakshineswar \\
\hspace*{0pt}\hfill Kolkata, West Bengal, Pin ‐ 700076, India \\
\hspace*{0pt}\hfill Mobile : +91‐8697785380 \\
\hspace*{0pt}\hfill Email : \href{mailto:debjitpal5040@gmail.com}{\custombold{debjitpal5040@gmail.com}} \\
\hspace*{0pt}\hfill Website : \href{https://debjitpal5040.github.io}{\custombold{https://debjitpal5040.github.io}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{Aug 2021-now} \runsubsection{GirlScript Winter Of Contributing}\\
\descript{Open Source Contributor}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I am contributing here for world's largest multilingual repository.
\descriptright{Git, Github}
\end{minipage}
\sectionsep
\datecolor{Jun 2021-Jul 2021} \runsubsection{IASc‐INSA‐NASI Summer Research Fellowship}
\descript{Research Intern}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I worked under Dr. Venky Krishnan Sir, faculty of TIFR Centre for Applicable Mathematics, Bangalore. My research topic was Real Analysis and Point Set Topology.\\
\descriptright{Real Analysis, Set theory, Topology}
\end{minipage}
\sectionsep
\datecolor{Mar 2021-Jul 2021} \runsubsection{KGEC Summer Of Code}
\descript{Open Source Contributor}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I contributed to two GitHub repositories namely heart‐saver and Space‐Missions where I helped to develop a website to predict heart attack 1and a notebook containing detailed data analysis of Space missions respectively.\\
\descriptright{ML, Web Development, Python, HTML, CSS, Git, GitHub}
\end{minipage}
\sectionsep
\datecolor{Mar 2021-May 2021} \runsubsection{GirlScript Summer Of Code}
\descript{Open Source Contributor}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I contributed to Master PyAlgo GitHub repository where I wrote and documented codes for applications of some well known algorithms.\\
\descriptright{Algorithms, Python, Git, GitHub}
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements/Awards} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2021} \runsubsection{CodeChef}
\descript{Competitive Programming}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I am a 3 star coder at CodeChef.
\end{minipage}
\datecolor{2021} \runsubsection{HackerRank}
\descript{Competitive Programming}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I am a 5 star Python coder at HackerRank.
\end{minipage}
\datecolor{2019} \runsubsection{Engineering, WBJEE}
\descript{Securing Rank}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I secured General Merit Rank (GMR) 1385 in my state engineering entrance exam WBJEE.
\end{minipage}
\datecolor{2019} \runsubsection{B.Math, ISI Bangalore}
\descript{Entrance Exam}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
I cleared the ISI B.Math Entrance exam.
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Side Project}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2021} \runsubsection{Simple Calculator app}
\descript{Swift, Xcode, iOS, iPadOS}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
I developed a basic calculator app for iOS and iPadOS.
\end{minipage}
\datecolor{2021} \runsubsection{ML Algorithms}
\descript{Machine Learning, Python, Jupyter Notebook}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
I developed a repository on codes and documentation of important machine learning algorithms.
\end{minipage}
\datecolor{2021} \runsubsection{WhatsApp Chat Analysis}
\descript{Data Analysis, Python}
\noindent
\hspace{4em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
I made a data analysis on a WhatsApp group chat.
\end{minipage}
\end{minipage} 
\end{document}  \documentclass[]{article}